### 2016-04-21 doc/publications/plos16/plos16.tex
Added RF numbers to table

For example, the 1000 Genome data consists of approximately 2500 samples with up to 80 million variants~\cite{1KG2012}, denoting the differences between individuals. 
This dataset consumes close to a terabyte of disk space.
The richness of this data can be utilised in other datasets as well by filling in or "imputing" the information at genomic positions previously unobserved due to the less detailed resolution of older array technology [citation about imputation]. 
This means that the large number of samples for which genome-wide association (GWA) data is available~\cite{Welter2013} can be extended horizontally by imputing the previously unobserved genotypes. 
This provides the potential to generate datasets of hundreds of thousands of individuals with millions of variants, highlighting the need for incorporating modern compute paradigms to deal with these challenges.

@@

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Performance comparison between the different Machine Learning algorithms.}}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
\bf{Genome \%}  & \bf{method} & \bf{Accuracy} & \bf{Runtime (s)} & \bf{Memory} \\
\hline
X\% & CursedForest & &  &\\ \hline
          & RF(Spark ML) & &  &\\ \hline
          &  RF(R) & &  &\\ \hline
          &  LR & &  &\\ \hline
XX\% & CursedForest & &  &\\ \hline
          & RF(Spark ML) & &  &\\ \hline
          &  RF(R) & &  &\\ \hline
          &  LR & &  &\\ \hline

100\% & CursedForest & & & \\ \hline
          & RF(Spark ML) & &  &\\ \hline
          &  RF(R) & &  &\\ \hline
          &  LR & &  &\\ \hline
          & kmeans(Spark ML) & & & \\ \hline
\end{tabular}
\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
%\end{adjustwidth}
\end{table}

>>>>

For example, the 1000 Genome data consists of approximately 2500 samples with up to 80 million variants~\cite{1KG2012}, denoting the differences between individuals. 
This dataset consumes close to a terabyte of disk space.
The richness of this data can be utilised in other datasets as well by filling in or ``imputing" the information at genomic positions previously unobserved due to the less detailed resolution of older array technology [citation about imputation]. 
This means that the large number of samples for which genome-wide association (GWA) data is available~\cite{Welter2013} can be extended horizontally by imputing the previously unobserved genotypes. 
This provides the potential to generate datasets of hundreds of thousands of individuals with millions of variants, highlighting the need for incorporating modern compute paradigms to deal with these challenges.

@@

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Performance comparison between the different Machine Learning algorithms.}}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
\bf{Genome \%}  & \bf{method} & \bf{Accuracy} & \bf{Runtime (s)} & \bf{Memory/Node} \\
\hline
8\% (chr1) & CursedForest & 0.0359 & 1hr 58min 23sec & 4GB \\ \hline
          & RF(Spark ML) & 0.0395 & 8hr 29min 07sec & 8GB \\ \hline
          &  RF(R) & &  &\\ \hline
          &  LR & &  &\\ \hline
XX\% & CursedForest & &  &\\ \hline
          & RF(Spark ML) & &  &\\ \hline
          &  RF(R) & &  &\\ \hline
          &  LR & &  &\\ \hline

100\% & CursedForest & 0.0231 & 7hr 14min 40sec & 8GB \\ \hline
          & RF(Spark ML) & - & - & - \\ \hline
          &  RF(R) & &  &\\ \hline
          &  LR & - & - & - \\ \hline
          & kmeans(Spark ML) & & & \\ \hline
\end{tabular}
\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
%\end{adjustwidth}
\end{table}
